Contracts for Contracts

### 2023-06-06 paper/introduction.tex
paper
misc

Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
design-by-contract methodology \cite{DBLP:conf/tools/Meyer98a}, various styles
of behavioral contracts have been widely adopted in Java, Haskell, C\#, Python,
Racket, Elixir \cite{DBLP:conf/erlang/0001BBHMEF22}, etc. \note{cite}
In this paper, we develop a behavioral contract system \lang for the Solidity
language, providing a practical specification and monitoring system
for both higher-order and temporal behaviors.
Solidity is a programming language to build smart contract programs that run on
the Ethereum platform.  As one of the most popular ecosystem of smart
contracts, Solidity has been used \todo{to do cool things}.

@@

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
  \item We design \lang, an extension for Solidity that allows programmers to
        specify and enforce higher-order and temporal behaviors in smart contracts.
        We demonstrate \lang's use cases through extensive examples and
        implement \lang as a preprocessor for ordinary Solidity programs.
	\item We present the core formalization $\lambda_\lang$ for our proposed
	      extension, including its syntax, formal semantics, compilation, and
	      soundness.
  \item We examine a number of real-world attacks with \lang, showing that our
        approach is effective in improving safety and reliability of smart contract
        programs.
  \item We evaluate the overhead of \lang compared to manually implemented
        assertions and checks, showing that our approach does not introduce
        additional runtime overhead.
\end{itemize}

>>>>

Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
design-by-contract methodology \cite{DBLP:conf/tools/Meyer98a}, various styles
of behavioral contracts have been widely adopted in Java, Haskell, C\#, Python,
Racket, Elixir \cite{DBLP:conf/erlang/0001BBHMEF22}, etc. \note{cite}
In this paper, we develop a behavioral contract system \lang (Contract Solidity) for the Solidity
language, providing a practical specification and monitoring system
for both higher-order and temporal behaviors.
Solidity is a programming language to build smart contract programs that run on
the Ethereum platform.  As one of the most popular ecosystem of smart
contracts, Solidity has been used \todo{to do cool things}.
\todo{explain challenges}

@@

\paragraph{Contributions} This paper makes the following contributions:
\begin{itemize}
  \item We design \lang, an extension for Solidity that allows programmers to
        specify and enforce higher-order and temporal behaviors in smart contracts.
        We demonstrate \lang's use cases through extensive examples and
        implement \lang as a preprocessor for ordinary Solidity programs.
	\item We present the core formalization $\lambda_\lang$ for our proposed
	      extension, including its syntax, formal semantics, compilation, and
	      soundness.
  \item We examine a number of real-world attacks with \lang, showing that our
        approach is effective in improving safety and reliability of smart contract
        programs.
  \item We evaluate the overhead of \lang compared to manually implemented
        assertions and checks, showing that our approach does not introduce
        additional runtime overhead.
\end{itemize}
